---
title: "Sidebar in boxes?"
author: "David Granjon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sidebar in boxes?}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## box sidebar: Getting started

`{shinydashboardPlus}` comes with a new customization in the `box()` function to allow you to create sidebar inside boxes:

```{r, eval=FALSE}
library(shiny)
library(shinydashboard)
library(shinydashboardPlus)
 
 shinyApp(
  ui = dashboardPage(
    header = dashboardHeader(),
    body = dashboardBody(
      box(
        title = "Update box sidebar", 
        closable = TRUE, 
        width = 12,
        height = "500px",
        solidHeader = FALSE, 
        collapsible = TRUE,
        actionButton("update", "Toggle card sidebar"),
        sidebar = boxSidebar(
          inputId = "mycardsidebar",
          p("Sidebar Content")
        )
      )
    ),
    sidebar = dashboardSidebar()
  ),
  server = function(input, output, session) {
    observe(print(input$mycardsidebar))
    
    observeEvent(input$update, {
      updateBoxSidebar(inputId = "mycardsidebar")
    })
    
  }
 )
```

<video width="640" height="480" controls style="display: block; margin: 0 auto;">
  <source src="figures/boxPlus-sidebar.mp4" type="video/mp4">
</video>

To toggle the sidebar, click on the **i** icon next to the collapse
and close icons.

You can currently modify the width and the background color of the box sidebar.
The _startOpen_ argument allow you to control if the sidebar should
be opened or collapsed at start. The box sidebar works very well to embed inputs elements such as slider inputs, as in the example above. Never use the sidebar when the box body is empty, since the sidebar height depends on the body height. 


## Notes
When including an image in the box sidebar and to make sure it is correctly displayed,
you have to add a *style* attribute to the img tag as follows:
```r
img(style = "width: 100%; height: 100%;", src = "http://i.imgur.com/aBayW5C.png")
```