---
title: "Using the rightSidebar"
author: "David Granjon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the rightSidebar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## The controlbar

The template below will create the most basic shinydashboardPlus page:

```{r, eval=FALSE}
library(shiny)
library(shinydashboard)
library(shinydashboardPlus)
shinyApp(
  ui = dashboardPage(
    header = dashboardHeader(),
    sidebar = dashboardSidebar(),
    body = dashboardBody(),
    controlbar = dashboardControlbar(),
    title = "DashboardPage"
  ),
  server = function(input, output) { }
)
```

The `dashboardControlbar` function takes the following arguments:

- skin: you can display it either in light or dark mode
- Fill it with `controbarMenu`. You can include inputs,
text or custom HTML elements.
- In the `dashboardHeader()` function, you can customize the controlbar trigger.

<video width="640" height="480" controls style="display: block; margin: 0 auto;">
  <source src="figures/right-sidebar.mp4" type="video/mp4">
</video>

<br>

```{r, eval=FALSE}
shinyApp(
   ui = dashboardPage(
     header = dashboardHeader(),
     sidebar = dashboardSidebar(),
     body = dashboardBody(),
     controlbar = dashboardControlbar(
      skin = "dark",
      controlbarMenu(
       id = "menu",
       controlbarItem(
        "Tab 1",
        "Welcome to tab 1"
       ),
       controlbarItem(
        "Tab 2",
        "Welcome to tab 2"
       )
      )
     ),
     title = "Right Sidebar"
   ),
   server = function(input, output) { }
 )
```

It is best practice to limit the number of `controlbarItem` to 5.