---
title: "CSS preloaders"
author: "David Granjon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CSS preloaders}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(shiny)
library(shinydashboard)
library(shinydashboardPlus)
library(waiter)
```

## How to set up a preloader?

Pass the argument `preloader` to the `dashboardPage()` function. It expects a nested list:

  - waiter is a sub-list containing all parameters necessary to `waiter::waiter_show_on_load`
  - duration is the loader timeout in seconds. We usually use milliseconds in JavaScript but 
  `shiny::showNotifications` expects seconds.
  
Please have a look to the `{waiter}` [documentation](https://waiter.john-coene.com/) for more details.

That's all!

```{r waiter-code, eval=FALSE}
shinyApp(
  ui = dashboardPage(
    preloader = list(
      waiter = list(html = tagList(spin_1(), "Loading ..."), color = "#3c8dbc"),
      duration = 5
    ),
    header = dashboardHeader(),
    sidebar = dashboardSidebar(),
    body = dashboardBody(
      actionButton("reload", "Reload")
    ),
    title = "Preloader"
  ),
  server = function(input, output, session) {
    # fake reload
    observeEvent(input$reload, {
      session$reload()
    })
  }
)
```

<div class="marvel-device ipad black">
<div class="camera"></div>
<div class="screen">
<iframe width="100%" src="https://dgranjon.shinyapps.io/shinydashboardPlus-preloader/" allowfullscreen="" frameborder="0" scrolling="no" height="770px"></iframe>
</div>
<div class="home"></div>
</div>
